\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-21 WOOT/Files/related_work.tex
REVISION OF RELATED WORK

In this part, we survey related works on USB attack in Section III-A, and USB defence security in Section III-B, respectively.

\subsection{USB Attack}
While many USB based attacks have been developed, these attacks are all tied to the environment of the target devices. In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transformation interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received. One way is to masquerade protocol of attack devices, e.g., Rubbery Ducky\cite{rubber},\cite{badusb}, \cite{rubberducky2020}, \cite{usbbypassing}, \cite{iseeyou}and USBderivery\cite{usbdriver}, when they are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying. Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modified the USB table with an additional RF transmitter. What is more, the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technology. These attacks are all using the vulnerabilities of the protocol of USB, but due to the limitations of USB 2.0, there are no port for video transformation in the devices with USB 2.0, so it is impossible to handle the real-time screen information of the host, only environment fitted commands and scripts will work in these scenarios, as well as the attack time.

@@

\subsection{USB Defence Security}
There are already some defenses against BadUSB attacks. 
And there has been a comprehensive investigation of previous work.\cite{sok}.
BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
without these special pins, data can't be transferred in the USB cable. USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host. At this case, `D-' and `D+' are disabled.
However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging. Pham et al. \cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code over malicious devices from attacking host.
There are also some work like TMSUI\cite{yang2015tmsui}, which based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.

>>>>

In this part, we survey related works on USB attack in Section~\ref{subsec:usb_attack}, and USB defence security in Section \ref{subsec:usb_defence}, respectively.

\subsection{USB Attack}
\label{subsec:usb_attack}
While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices. In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received. One way is to masquerade protocol of attack devices, e.g., Rubbery Ducky\cite{rubber},\cite{badusb}, \cite{rubberducky2020}, \cite{usbbypassing}, \cite{iseeyou}and USBderivery\cite{usbdriver}, when they are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying. Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modified the USB table with an additional RF transmitter. What is more, the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technology. These attacks are all using the vulnerabilities of the protocol of USB, but due to the limitations of USB 2.0, there are no port for video transformation in the devices with USB 2.0, so it is impossible to handle the real-time screen information of the host, only environment fitted commands and scripts will work in these scenarios, as well as the attack time.

@@

\subsection{USB Defence Security}
\label{subsec:usb_defence}
There are already some defenses against BadUSB attacks. 
And there has been a comprehensive investigation of previous work.\cite{sok}.
BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
without these special pins, data can't be transferred in the USB cable. USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host. At this case, `D-' and `D+' are disabled.
However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging. Pham et al. \cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code over malicious devices from attacking host.
There are also some work like TMSUI\cite{yang2015tmsui}, which based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.
